---
title: "parsing_for_coords"
author: "Emmanuel Oluloto"
date: "April 3, 2019"
output: html_document
---

```{r libs, include=FALSE}
library(tidyverse)
library(xml2)
library(dplyr)
```

## SQL File to Javascript/JSON

We found a great sql file with all the countries [here](https://stackoverflow.com/questions/21302002/google-map-as-a-vector-map). However we would like to have an object storing all country polygon paths containing all the arrays in JavaScript form. The objective is to create and edit polygons as we need them, as well as obtain values from them. We cannot use KML, as we cannot really alter individual polygons drawn with a KML layer.    

Thus we will be using the file to create the JS code we need using string parsing functions in R. We will use the unique country abbreviations as keys in our country object.

### SQL to CSV
To play with files in R, we need them in a standard R format, like a CSV. To convert the SQL to a CSV, we used [this site](https://www.rebasedata.com/convert-mysql-to-csv-online).    

[This site](https://www.eversql.com/sql-syntax-check-validator/) is also useful for checking SQL code validity. 


### CSV to JS
We now have the CSV file which we can import and alter.

#### Other Table Information
To get access to the capitals and other data, we will be importing another CSV and fusing it to the *countryData* dataframe.


```{r}
countryData = read_csv("datasets/gmaps_countries.csv")
colnames(countryData)

extraCountryData = read_csv("datasets/country-capitals.csv")
colnames(extraCountryData)


allCountryData <- merge(countryData, extraCountryData, by.x = "iso", by.y = "CountryCode")
#countryData = allCountryData

countrySample <- head(allCountryData, 12)
#countrySample
```
The *description* field contains the coordinates we need. There is a LOT of text in the geometry fields of each row, so we will start by only looking at the first 12 rows of our dataset.


#### Geometry Field Breakdown
The geometry field is written in KML. Thus, geo-elements are denoted and separated by opening and closing tags.

+ A simple polygon is usually denoted by *<Polygon><outerBoundaryIs><LinearRing><coordinates>...</coordinates></LinearRing></outerBoundaryIs></Polygon>*  
+ A multi-polygon OR polygon with holes is denoted by *<MultiGeometry><Polygon>...*. This could also be just one polygon. 

We need to test for different cases and plan accordingly.

### Split Strings 
Let's test R's string functions using just one of our 12 samples. 
We will split the string in the geometry field to get just the coordinates as a string.
```{r, poly_case}
countrySample[1,]

#Geo-field
countrySample[1,7]
countrySample$geometry[1]

# Turn field to string -> parce w xml lib -> get all coordinate sub-nodes -> Get node content
polycoord <- countrySample$geometry[1] %>% toString() %>% read_xml() %>% xml_find_all(".//coordinates") %>% xml_text()
#polycoord
str_sub(polycoord, 1, 20)

# Get individual lat-lng values
coord_list = strsplit(polycoord, " ")

# But wait! In KML, Lat-Lng is switched! So we have to split and recombine!
lats_lngs = strsplit(coord_list[[1]], ",")
correct = lapply(lats_lngs,  function(x){paste(x[2], x[1], sep = ",")})

coord_list = correct
```

We have the individual latitudes and longitudes! We can then print out our JS code:

```{r poly_Case2}
# Generate JS string
js_code = paste("{ '", countrySample$iso[1], "': [ ")
co = ""

# for(i in coord_list){ print(i)}

# Concatenate into mega-string
for(i in coord_list){
  #for(j in i){
    co = paste(co, " new google.maps.LatLng(", i, "),\n")
  #}
  # Remove last ", " from file
  
}
co = substr(co, 1, nchar(co)-2)


js_code = paste("var testCountry = ",js_code, co, " ] };")
#js_code
str_sub(js_code, 1, 20)

# Making sure last digits are correct
str_sub(js_code, -12, -1)
```

### Exporting to Text

The **cat** function is reall helpful for helping us export our generated code to a file.
```{r}
# Does not work with formatting text with newlines-_-
#write.table(js_code, "mylatlng.js", sep="\t")



cat(js_code, file = "js_files/mylatlng.js")
```

Our code prints out successfully!
But what if our polygon uses more than 1 path?


### Parsing Multigons
If there is more than 1 *coordinates* opening/closing pair, then the **xml_find_all** function should return more than 1 list. Let's test with the 9th country in the list, *Argentina*.
```{r multi_poly}
polycoords <- countrySample[9,7] %>% toString() %>% read_xml() %>% xml_find_all(".//coordinates") %>% xml_text()
length(polycoords)

coord_lists = strsplit(polycoords, " ") 

# Re-flip lat-long
# There might be a cleaner way to do this with nested lapply
correct = list()
for(co_list in coord_lists){
  lats_lngs = strsplit(co_list, ",")
  corr_list = unlist(lapply(lats_lngs,  function(x){paste(x[2], x[1], sep = ",")})) # THIS IS A VECTOR, NOT A LIST
  #print(corr_list)
  #correct <- append(correct, list(corr_list))
  correct[[length(correct) + 1]] = corr_list
}



coord_lists = correct
str(coord_lists)
#str(correct)
```

```{r TESTING, eval=FALSE, include=FALSE}
polycoords <- countrySample[9,7] %>% toString() %>% read_xml() %>% xml_find_all(".//coordinates") %>% xml_text()
length(polycoords)

coord_lists = strsplit(polycoords, " ") 

# Re-flip lat-long
# There might be a cleaner way to do this with nested lapply
correct = list()
#for(co_list in coord_lists){
co_list = coord_lists[[1]]
  lats_lngs = strsplit(co_list, ",")
  corr_list = lapply(lats_lngs,  function(x){paste(x[2], x[1], sep = ",")})
  #print(corr_list)
  #correct <- append(correct, list(corr_list))
  #correct[[length(correct) + 1]] = corr_list
#}

#coord_lists = correct
str(coord_lists)
str(correct)
```

Argentina has a lot of tiny peices! Let's see how we can account for all of them.
Using a *for loop* to apply our concatenation operation to each list of strings should be helpful. We will store different polygons in different arrays, all of which will be within an array.

```{r multi_poly2}
# Generate JS string
more_code = paste("{ '", countrySample[9,1], "': [ ")
co = ""


  for(list in coord_lists){
    # Beginning of path array
    co = paste(co, "[")

    for(j in list){
      co = paste(co, " new google.maps.LatLng(", j, "),\n")
    }
    
    # Remove last ", " from file
    co = substr(co, 1, nchar(co)-2)
    # Annoying error
    co = paste(co, "],\n")

  }
co = substr(co, 1, nchar(co)-2)

more_code = paste("var longTest = ", more_code, co, " ] };")
#more_code
str_sub(more_code, 1, 50)

# Making sure last digits are correct
str_sub(more_code, -12, -1)

cat(more_code, file = "js_files/morelangslngs.js")
```

### Applying Function to CSV Rows

Now that we know our function is working, we can modify it to go through the rows in our dataset. We ill be storing the generated code of each file in a corresponding column position as well as writing the code to a js file.     


We'll be doing this with just the 12 countries in the sample. After seeing how well the code works in our actual web application, we can then run the code for all of them! We will also have to add some more info to the table denoting capital information and anything else we would like to add.

```{r code_function}

# Remove last characters
removeLastChars <- function(string, count){
  return(substr(string, 1, nchar(string)-count))
}

# Flip long-lat order of list of lists
flipCoords <- function(listOfCoordLists){
  correct = list()
  for(list in listOfCoordLists){
    lats_lngs = strsplit(list, ",")
    corr_list = unlist( lapply(lats_lngs,  function(x){paste(x[2], x[1], sep = ",")}) )
    correct[[length(correct) + 1]] = corr_list
  }
  
  return(correct)
}

parse_to_JS <- function(dataset,colID=7,createColumn=TRUE) {
  all_code = "var countryPaths = \n{"
  dataset$js_code = NA
  # Run through all rows
  for (row in 1:nrow(dataset)) {
    kml = dataset[row, colID]
    
    # Beginning of file
    more_code = paste(" '", toString(dataset$iso[row]), "': [ ", sep="")
    #toString(dataset[row, 3])
    co = ""

    # Split string into individual pairs
    polycoords <- kml %>% toString() %>% read_xml() %>% xml_find_all(".//coordinates") %>% xml_text()
    coord_lists = strsplit(polycoords, " ")
    coord_lists = flipCoords(coord_lists)
    
    for(list in coord_lists){
      # Beginning of path array
      co = paste(co, "[")
      # Add newlines only at certain intervals
      counter = 1
      for(j in list){
        
        co = paste(co, " new google.maps.LatLng(", j, "),")
      if(counter%%3 ==0) co = paste(co, "\n") else co = paste(co, " ")
        #print(counter%%3 ==0)
        #print(str_sub(co, -8, -1))
        counter = counter + 1
        
      }
    
      # Remove last ", " from inner array for 1 path for a country
      co = removeLastChars(co, 3)
      # End of path array
      co = paste(co, "],\n")

    }
    # Remove last ", " from outer array for all paths for 1 country
    co = removeLastChars(co, 2)
    # Add code for entire row to file
    more_code = paste(more_code, co, " ] ,\n")
    # Store code for each country back in table
    if(createColumn) dataset$js_code[row] = more_code
    all_code = paste(all_code, more_code)
  } # end of iterating through arrays
  
  # Remove last ", " from overall JS object
  all_code = removeLastChars(all_code, 2)
  all_code = paste( all_code, "  };")
  return(all_code)
} # function end



# Test function
test = parse_to_JS(countrySample)
str_sub(test, -12, -1)
cat(test, file = "js_files/shapesTest.js")
```

Thsi snippet generates code for ALL the countries! This code will take a while to run.
```{r code_generation, eval=FALSE}
# This will take a WHILE, so do not auto-evaluate
shapes = parse_to_JS(countryData)
cat(shapes, file = "js_files/countryShapes.js")
```



## Generating Code for Markers and Arrays

We still need to generate code for the other properties of world countries, such as capital cities, coordinates, and available countries. This could also be a JSON file.

We will also need the list of country abbreviations which are available in our code.
```{r other_code}
# Test with 1 entry
countryInfo = ""
countryInfo = paste("{ '", countrySample$iso[11], "': { ", sep = "")

countryInfo = paste(countryInfo, "\n  countryName: '", countrySample$CountryName[11], "', \n")
countryInfo = paste(countryInfo, " landArea: ", countrySample$landarea[11], ", \n")
countryInfo = paste(countryInfo, " capital: '", countrySample$CapitalName[11], "', \n")
countryInfo = paste(countryInfo, " capital_location:  new google.maps.LatLng(", countrySample$CapitalLatitude[11], ",", countrySample$CapitalLongitude[11], "), \n")
countryInfo = paste(countryInfo, " continent: '", countrySample$ContinentName[11], "', \n")
countryInfo = paste(countryInfo, " color: '", countrySample$color[11], "' \n")

countryInfo = paste(countryInfo, " }  } ", sep = "")

cat(countryInfo, file = "js_files/AU_Info.js")
```


Now let's create the code for a dataframe!
```{r generate_country_info}

parse_code_to_JS <- function(dataset,createColumn=TRUE) {
  # List of country IDs in our dataset
  #countryIDs = apply(dataset$iso, 2, paste, collapse=", ")
  
  countriesInfo = "var countryInfo = \n{  \n"
  for (row in 1:nrow(dataset)) {
    # Start
    countryObject = paste("'", dataset$iso[row], "': { \n", sep = "")
    countryObject = paste(countryObject, "  countryName: ", shQuote(dataset$CountryName[row]), ", \n", sep = "")
    countryObject = paste(countryObject, "  landArea: ", dataset$landarea[row], ", \n", sep = "")
    countryObject = paste(countryObject, "  capital: ", shQuote(dataset$CapitalName[row]), ", \n", sep = "")
    countryObject = paste(countryObject, "  capital_location:  new google.maps.LatLng(", 
                        dataset$CapitalLatitude[row], ",", 
                        dataset$CapitalLongitude[row], "), \n", sep = "")
    countryObject = paste(countryObject, "  continent: ", shQuote(dataset$ContinentName[row]), ", \n", sep = "")
    countryObject = paste(countryObject, "  color: ", shQuote(dataset$color[row]), " \n", sep = "")
    # End
    countryObject = paste(countryObject, "},\n", sep = "")
    
    countriesInfo = paste(countriesInfo, countryObject)
    
  }
  countriesInfo = removeLastChars(countriesInfo, 2)
  countriesInfo = paste(countriesInfo, "\n} ", sep = "")
  
  #print(countryIDs)
  return(countriesInfo)
}

test = parse_code_to_JS(allCountryData)
cat(test, file = "js_files/countryInfo.js")
```


```{r}
#countryIDs = apply(countrySample$iso, 2, paste, collapse=", ")
countryData = countrySample
#countryData = allCountryData

abbrArray = "var validPolys = [ "
for(r in 1:nrow(countryData)){
  if(!is.na(countryData$geometry[r]) )
    abbrArray = paste(abbrArray, shQuote(countryData$iso[r]), ",", sep="")
  if(r %% 20 == 0)
    abbrArray = paste(abbrArray, "\n")
  if(r == nrow(countryData))
    abbrArray = removeLastChars(abbrArray,1)
}

abbrArray = paste(abbrArray, " ];\n\n")
#cat(abbrArray, file = "js_files/arrays.js")

#abbrArray = ""
abbrArray = paste(abbrArray, "var validCapitals = [ ")
for(r in 1:nrow(countryData)){
  #print(is.numeric(countryData$CapitalLatitude[r]) & is.numeric(countryData$CapitalLongitude[r]))
  if( !is.na(countryData$CapitalLatitude[r]) & !is.na(countryData$CapitalLongitude[r]) )
    abbrArray = paste(abbrArray, shQuote(countryData$iso[r]), ",", sep="")
  if(r %% 20 == 0)
    abbrArray = paste(abbrArray, "\n")
  if(r == nrow(countryData))
    abbrArray = removeLastChars(abbrArray, 1)
}


abbrArray = paste(abbrArray, " ];\n")
cat(abbrArray, file = "js_files/arrays.js")
```


#### Save Final DB

To inspect the database, we can save the final dataset to a CSV.
```{r}
write.csv(allCountryData, file = "allCountryData.csv")
```

